% YAAC Another Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/yaac-another-awesome-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

%Section: Work Experience at the top

% Margaux Filippi edits
% Note: I commented out all the \emptySeparator between sections
% \emptySeparator
  
\sectionTitle{Experience}{}

\begin{experiences}
  \experience
    {2022/07 - 2023/11} {Senior Principal Engineer}{Our Next Energy (ONE)}{Fremont, CA}
    { } {
        \begin{itemize}
        \item Developed ML-based solutions to accelerate R\&D for battery manufacturing. 
        \begin{itemize} % for subitem
            \item Developed a predictive model for battery life with 10\% MAPE compared to 16\% in state-of-the-art academic literature.
            \item Projects included predictive models to increase factory throughput and CV algorithms for materials science automation.
            \end{itemize}
            
        \item Led the buildup of the cell lab and built software to automate cell testing, increasing throughput by orders of magnitude.                                           
        \end{itemize}
                    }
                    {}

  \experience
    {2022/02 -- 2022/06} {Ocean Program Manager \& Technical Lead}{Open Earth Foundation}{Remote / Los Angeles, CA}
    { }    {
    \begin{itemize}
        \item Set up and managed the Ocean Program to leverage AI for marine conservation.                      
        \item Created technical methodologies, including ML proof-of-concepts, for the issuance and verification of ecosystem credits.
                      \end{itemize}
                    }
        {}

  \experience
    {2021/11 -- 2022/01}     {Computer Vision Engineer}{Numina}{Remote / Brooklyn, NY}
    { }    {
        \begin{itemize}
            \item Upgraded ML pipelines, leading to a 13\% average accuracy improvement in 3 months.
            \item Created technological roadmaps and trained an ML engineer in Computer Vision.
        \end{itemize}
                    }
        {}

    \experience
    {2021/01 -- 2021/11} {Director of Ocean Science}{Running Tide Technologies, Inc.}{Remote / Portland, ME}
    {2020/03 -- 2021/01}    {
    \normalsize{Data Scientist / Oceanographer}
    \small
    \begin{itemize}
    \item Designed, developed and deployed CV and ML models to automate and scale production.
 \item Co-designed the machine vision systems for image acquisition and processing.
    \item Directed the ocean science research for the development and scaling of macroalgae-based carbon capture.
    \begin{itemize}
	\item Designed and oversaw field pilot experiments, leading an %diverse,
 interdisciplinary scientific and operational team.
	\item Conducted geospatial analyses and oceanographic simulations to guide site selection.
        \end{itemize}
    \end{itemize}
                    }
        {}
        
    \experience
    {2019/09 -- 2021/11} {Affiliate Researcher}{Environmental Dynamics Lab (ENDLab),  MIT}{Cambridge, MA}
    {2013/06 -- 2019/05}    {
    \normalsize{Graduate Research Assistant}
    \small
    \\\emph{Sc.D. advisors: I. Rypina, WHOI department of Physical Oceanography \& T. Peacock, ENDLab}
\\\emph{M.S. advisors: T. Peacock, ENDLab \& J.-L. Thiffeault, UWisc. - Madison department of Mathematics}
    
\begin{itemize}
    \item Developed unsupervised machine learning methods to reduce sensitivity to user biases, with applications to oceanic flows.
    \item Designed and conducted laboratory and field experiments, using CV analyses for dye plumes, fluid flows and object tracking.
    \item Senior mentor \& student-executive in a machine shop; teaching assistant for multiple academic and professional courses.
 \end{itemize}
                    }
        {}

    \experience
    {2019/07 -- 2019/09} {R\&D Contractor}{ARPA-E MARINER program, U.S. Department of Energy}{Remote / Washington, D.C.}
    { }    {
    
    \begin{itemize}
        \item Conducted satellite-based geospatial R\&D and oceanographic simulations for a macroalgae-based carbon capture project.
        \end{itemize}
                    }
        {}

    \experience
    {2012/06 -- 2013/05} {Junior Oceanographer}{Sea Engineering, Inc.}{Waimanalo, HI}
    {2011/02 -- 2012/05}    {
    \normalsize{Ocean Engineering Intern (part-time)}
    \small
    
    \begin{itemize}
        \item Field scientist and engineering assistant for various projects, aiding with field work, drafting and flow simulations. 
        \end{itemize}
                    }
        {}
        
\end{experiences}
